From Education to Entrepreneurship

### 2014-12-07 index.Rmd
Added formatted Zelig tables and began explanation of results

Controlling for country-specific effects,

@@

############ Running a regression with full df (including omitted variables)
RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

@@

# Run a least squares regression with Zelig
Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")

@@

# Plot simulation

@@

CI_omitted <- na.omit(CI)

# Regression equation with imputed values
Z2 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")

@@

@@

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}

par(mfrow = c(1, 2))
plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurial Intention', main = "Unimputed")
plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurial Intention', main = "Imputed")

>>>>

Our original intention was to conduct a country- the relationship between the way of teaching and the rate of entrepreneurship in each OECD country.  To do so, we should run a fixed effects regression for each country.  When doing so, however, we find that our explanatory variable has a negative coefficient and our regression equation contains a negative slope.  This may be due to a lack of available data, a flawed survey method, or inaccurate expectations.

@@

############ Running a regression with full df (including omitted variables)
RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

@@

# Run a least squares regression with Zelig
Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")

@@

@@

# Omit variables that could not be imputed by Adelia (b/c of lack of data)
CI_omitted <- na.omit(CI)

# Regression equation with imputed values
Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")

############ Set range of values for Z1 and Z2

@@

# Set range of WayofTeaching values in simulation
x.out3 <- setx(Z1, WayofTeaching = 1.353:3.278)

# Run simulation (default 1000 trials)
simz3 <- sim(Z1, x = x.out3)

# Set range of WayofTeaching values in simulation
x.out4 <- setx(Z2, WayofTeaching = 1.128:3.312)

# Run simulation (default 1000 trials)
simz4 <- sim(Z2, x = x.out4)

@@

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
library("Zelig")

# Set layout
par(mfrow = c(2, 2))

# Plot simz1 (unimputed)
plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner', main = "Unimputed")

# Plot simz2 (imputed)
plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner', main = "Imputed")

# Plot simz3 (unimputed)
plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner', main = "Unimputed")

# Plot simz4 (imputed)
plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner', main = "Imputed")
